Generating a README.txt file for the Dryad submission of data from study "DateLife: leveraging databases and analytical tools to reveal the dated Tree of Life

### 2022-07-18 dryad/README.Rmd
removing row number column from csv files for dryad upload

file.copy(from = "../tables/table-fringillidae-small-example.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_table_1.csv")
file.copy(from = "../tables/table-fringillidae-small-example-summary.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_table_2.csv")
file.copy(from = "../tables/table-fringillidae-all-congruified.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_supplementary_table_S1.csv")
file.copy(from = "../tables/table-fringillidae-all-congruified.pdf",
          to = "../dryad/Sanchez-Reyes_etal_2022_supplementary_table_S1.pdf")
file.copy(from = "../tables/table-fringillidae-all-summary.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_supplementary_table_S2.csv")
file.copy(from = ".../tables/table-fringillidae-all-summary.pdf",
          to = "../dryad/anchez-Reyes_etal_2022_supplementary_table_S2.pdf")
```

>>>>

file.copy(from = "../tables/table-fringillidae-small-example.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_table_1.csv",
          overwrite = TRUE)
file.copy(from = "../tables/table-fringillidae-small-example-summary.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_table_2.csv",
          overwrite = TRUE)
file.copy(from = "../tables/table-fringillidae-all-congruified.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_supplementary_table_S1.csv",
          overwrite = TRUE)
file.copy(from = "../tables/table-fringillidae-all-congruified.pdf",
          to = "../dryad/Sanchez-Reyes_etal_2022_supplementary_table_S1.pdf",
          overwrite = TRUE)
file.copy(from = "../tables/table-fringillidae-all-summary.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_supplementary_table_S2.csv",
          overwrite = TRUE)
file.copy(from = ".../tables/table-fringillidae-all-summary.pdf",
          to = "../dryad/anchez-Reyes_etal_2022_supplementary_table_S2.pdf",
          overwrite = TRUE)
```
